Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Add Introduction for Pollster Analysis
Add Introduction for Pollster Analysis

>>>>

# Pollster Analysis

The Marquette Law School Poll employs a rigorous methodology to survey adults in the US on national issues, incorporating probability-based sampling that combines Address-Based Sampling (ABS) and Stratified Random Sampling. This approach, including online and offline respondents, ensures broad representativeness. The SSRS Polling Panel supports participant recruitment, and weighting adjustments enhance result accuracy.

## What is the population, frame, and sample?

## How is the sample recruited?

## What sampling approach is taken, and what are some of the trade-offs of this?

## How is non-response handled?

## What is good and bad about the questionnaire?
